---
title: "Analysis_Laudine_R&R"
author: "Laudine Carbuccia"
date: "2025-01-20"
always_allow_html: true
language:
  label:
    fig: 'Figure '
    tab: 'Table '
    eq: 'Equation '
output: 
    bookdown::word_document2: 
      reference_docx: FormatRefWordFinal.docx
      fig_caption: yes
      toc: no
    officedown::rdocx_document:
---


```{r LoadLibraries, include=FALSE}
source(here("RScripts","LoadInstallPackages.R"), local = knitr::knit_global())
```

```{r LoadData, include=FALSE}
source(here("RScripts","LoadAllData.R"), local = knitr::knit_global())
```

```{r ImportAllFunctions, include=FALSE}
source(here("RScripts","AllFunctions.R"), local = knitr::knit_global())
```



```{r, include=FALSE, cache=FALSE}
knitr::read_chunk(here("RScripts","MainAnalyses.R"))
# This file contains all the chunks of codes to be called at the right place in the Rmarkdown document
```

# Comments from the reviewers

## Reviewer 1

### Comment 1
"One thing I missed was additional descriptive information (in the supplementary file), in particular distributions of all variables by SES, migration background, baseline knowledge, temporal orientation, previous childcare usage, activity status, and by district."

### Response

#### Distribution of all variables by SES 
```{r DiffEduc, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```


#### Distribution of all variables by migration background
```{r DiffMig, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

#### Distribution of all variables by baseline knowledge
```{r DiffInfo, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

#### Distribution of all variables by temporal orientation
```{r DiffPresentBias, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

#### Distribution of all variables by previous childcare usage
```{r DiffUse, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

#### Distribution of all variables by activity status
```{r DiffActive, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

#### Distribution of all variables by district
To perform the equality tests, we break down the comparison across districts in three parts: Paris vs. other districts, Seine-Saint-Denis vs. other districts, and Val de Marne. 

##### Paris vs. other districts
```{r DiffParis, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

##### Seine-Saint-Denis
```{r DiffSSD, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

##### Val de Marne
```{r DiffVDM, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```


### Comment 2

Furthermore, we know from previous research that SES, migration background, baseline knowledge, temporal orientation, previous childcare usage and activity status are correlated. It would be very useful to provide information to which degree this was the case to get a better understanding of the relevance of the different indicators of inequalities under view.

This plot shows the tetrachoric correlation coefficients of the different variables. We see that in any case we find perfect correlation.
```{r correlation, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

The strongest correlations were found between migration background and knowledge (-0.57), followed by knowledge and previous early childcare use (-0.55). This suggests that individuals with a migration background tend to exhibit lower baseline knowledge, while those who have previously utilized early childcare services demonstrate a higher level of knowledge.

Moderate correlations were observed between migration background and temporal orientation (-0.49), migration background and activity (-0.48), and between socioeconomic status (SES) and knowledge (0.47). SES also exhibited moderate positive correlations with activity (0.43) and temporal orientation (0.33), while displaying a negative correlation with migration background (-0.32).