---
title: "Power computations"
author: "Arthur Heim"
date: "2025-01-20"
always_allow_html: true
language:
  label:
    fig: 'Figure '
    tab: 'Table '
    eq: 'Equation '
output: 
    bookdown::word_document2: 
      reference_docx: FormatRefWordFinal.docx
      fig_caption: yes
      toc: no
    officedown::rdocx_document:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE, warning=FALSE,fig.width = 8,fig.height = 5,fig.pos = "H" #, 
#cache.lazy = FALSE)
)
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')

```

```{r LoadLibraries, include=FALSE}
library(here)
source(here("RScripts","LoadInstallPackages.R"), local = knitr::knit_global())
```

```{r LoadData, include=FALSE}
source(here("RScripts","LoadAllData.R"), local = knitr::knit_global())
```

```{r ImportAllFunctions, include=FALSE}
source(here("RScripts","AllFunctions.R"), local = knitr::knit_global())
```



# Hypothesis and simple formula

(Asymptotically Normal Estimator) We assume that the estimator $\hat{E}$ is such that there exists a constant (independent of $N) C(\hat{E})$ such that:

$$
\lim _{N \rightarrow \infty} \operatorname{Pr}\left(\frac{\hat{E}-E}{\sqrt{\mathbf{V}[\hat{E}]}} \leq u\right)=\Phi(u)
$$

with $\mathbf{V}[\hat{E}]=\frac{C(\hat{E})}{N}$.

A closed-form formula for power $\kappa$ is :

(Power with an Asymptotically Normal Estimator) With $\hat{E}$ asymptotically normal, and with $\beta_A>0$, we have:

- For a One-Sided Test: $H_0: E \leq 0 H_A: E=\beta_A>0$

$$
\kappa_{\text {oneside }}=\Phi\left(\frac{\beta_A}{\sqrt{\mathbf{V}[\hat{E}]}}-\Phi^{-1}(1-\alpha)\right)
$$

- For $\rightarrow$ Tyo-Sided Test: $H_0: E=0 H_A: E=\beta_A \neq 0$

$$
\kappa_{\mathrm{twoside}} \approx \Phi\left(\frac{\beta_A}{\sqrt{\mathbf{V}[\hat{E}]}}-\Phi^{-1}\left(1-\frac{\alpha}{2}\right)\right)
$$




```{r}
# functions
power <- function(betaA,alpha,varE){
  return(pnorm(betaA/sqrt(varE)-qnorm(1-alpha)))
}

power.twoside <- function(betaA,alpha,varE){
  return(pnorm(-betaA/sqrt(varE)-qnorm(1-alpha/2))+pnorm(betaA/sqrt(varE)-qnorm(1-alpha/2)))
}


CE.Encourage.fun <- function(pR,varYb,pE,p1D,p0D){
  return((1/pE)*(1/(p1D-p0D))^2*(((p1D*pR+p0D*(1-pR))/pR)^2*varYb/(1-pR)+((1-p1D*pR-p0D*(1-pR))/(1-pR))^2*var(yB)/pR))
}

MDE.Encourage.fun <- function(pR,varYb,pE,p1D,p0D,...){
  return(MDE(CE=CE.Encourage.fun(pR=pR,varYb=varYb,pE=pE,p1D=p1D,p0D=p0D),...))
}
# computing candidate participation rate, using the observed proportion below baryB
pEhat <- mean(E)
p1Dhat <- mean(Ds[E==1 & R==1])
p0Dhat <- mean(Ds[E==1 & R==0])

alpha <- 0.05
kappa <- 0.8

```


