---
title: "Investigating how administrative burden and search costs affect social inequalities
  in early childcare access, a randomised controlled trial"
author: "Supplementary Information for the manuscript  submitted to Nature Human Behaviour"
date: "2024-10-07"
bibliography: NHB.bib
csl: nature.csl
always_allow_html: true
language:
  label:
    fig: 'Figure '
    tab: 'Table '
    eq: 'Equation '
output: 
    bookdown::word_document2: 
      reference_docx: FormatRefWordFinal.docx
      fig_caption: yes
      toc: no
    officedown::rdocx_document:
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE, warning=FALSE,fig.width = 8,fig.height = 5,fig.pos = "H" #, 
#cache.lazy = FALSE)
)
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')

library(pacman)
p_load(here)
p_load(officedown)

```



```{r LoadLibraries, include=FALSE}
source(here("RScripts","LoadInstallPackages.R"), local = knitr::knit_global())
```

```{r LoadData, include=FALSE}
source(here("RScripts","LoadAllData.R"), local = knitr::knit_global())
```

```{r ImportAllFunctions, include=FALSE}
source(here("RScripts","AllFunctions.R"), local = knitr::knit_global())
```


```{r, include=FALSE, cache=FALSE}
knitr::read_chunk(here("RScripts","Appendix.R"))
```


# Early childcare supply in the areas

The average coverage rate in each district, including only the cities included in our sample, can be seen in Table \@ref(tab:DescriptiveAvgCoverageRate). The coverage rate is the number of available slot in a given area for 100 children aged 0-3 years.
The highest coverage rate is found in Paris, with 71.6 slots in 2021, and the lowest in Seine-Saint-Denis, with 38.5 slots. The average coverage rate in France in 2021 is 59.1 slots per 100 children aged 0-3 years.
In each district, the coverage rate is higher for daycare than for private childminders, with varying proportions in each districts. 


```{r DescriptiveAvgCoverageRate,echo=FALSE,results='asis', cache=TRUE, out.width='100%'}
```

This data can be compared to the average coverage rate in the whole districts in 2021 (i.e. including cities in which none of the households in our sample lived, but are in the same districts) in Table \@ref(tab:DescriptiveCoverageRateDaycareChildmindersDept). The results are about the same. The highest coverage rate is found in Paris, with 80.1 slots, and the lowest in Seine-Saint-Denis, with 34.5 slots. 

```{r DescriptiveCoverageRateDaycareChildmindersDept,echo=FALSE,results='asis', cache=TRUE,out.width='100%',}
```

The national coverage rates in daycare and private childminders can be found in Table \@ref(tab:DescriptiveCoverageRateDaycareChildmindersFrance). Our districts have a higher coverage rate in daycare than the national average, but a lower coverage rate in private childminders. Unlike in the districts included in our sample, the most available early childcare option in France is private childminders, with 27.3 slots per 100 children aged 0-3 years in 2021, compared to 26 slots in daycare. 


```{r DescriptiveCoverageRateDaycareChildmindersFrance,echo=FALSE,results='asis', cache=TRUE}
```

## Average effects of the information + support treatment on early childcare and daycare application and access by district

The effectiveness of our interventions varies substantially according to the local context. On the one hand, all effects on applications for low-SES households are concentrated outside of Paris, which could be consistent with a ceiling effect. In Paris, where the supply of early childcare in general and daycare specifically are the highest in France, inequalities were found to be very low in our sample and thus we found no effects of our intervention on application. On the other hand, all effects on daycare access for high-SES households were concentrated in Paris

### Early childcare
```{r HetCoverageRateEarlyChildcare,echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```



### Daycare
```{r HetCoverageRateDaycare,echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```


# Main results

## Heterogeneous effects of the information-only treatment on early childcare applications and access

```{r EarlyChildcareHetTableInformationOnly,echo=FALSE,out.width='120%', results='asis', cache=TRUE, out.width='100%',fig.cap="Heterogeneous effects of the information-only treatment on early childcare applications and access - Intention-to-treat estimates (ITT) estimates."}
```



## Heterogeneous effects of the information-only treatment on daycare applications and access

```{r DaycareTableInformationOnly,echo=FALSE,out.width='120%', results='asis', cache=TRUE, out.width='100%',fig.cap="Heterogeneous effects of the information-only treatment on early childcare applications and access - Intention-to-treat estimates (ITT) estimates."}
```


# Mechanisms
## Heterogeneous effects of the treatments on generic knowleged of the early childcare system
### Number of early childcare types known
```{r MechanismsGenericKnowledge,echo=FALSE,out.width='120%', results='asis', cache=TRUE}
```

### Knowledge that early childcare is subsidised
```{r MechanismsGenericKnowledgeSubsidies,echo=FALSE,out.width='120%', results='asis', cache=TRUE}
```

## Mechanims: Average effects of the information + support treatment on daycare application and access by activity of the mother at baseline
```{r MechanismsActive,  echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

# Robustness checks

## Sensitivity analysis of the main results: SES measurment
To ensure the robustness of the findings, we tested alternative definitions of socioeconomic status. Specifically, we considered mother's occupation using the International Socio-Economic Index of Occupational Status (ISEI) and a composite SES score that accounts for the highest occupation score and the highest education level in the household. As depicted below, the patterns of results remain constant with these definitions of SES.

### Information-only treatment

#### Heterogeneous effects of the information-only treatment on early childcare applications

```{r RobustnessHTESESGraphsT1EarlyChildcareApp,echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

#### Heterogeneous effects of the information-only treatment on early childcare access

```{r RobustnessHTESESGraphsT1EarlyChildcareAccess,echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

#### Heterogeneous effects of the information-only treatment on daycare applications

```{r RobustnessHTESESGraphsT1DaycareApp,echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```


#### Heterogeneous effects of the information-only treatment on daycare access

```{r RobustnessHTESESGraphsT1DaycareAccess,echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

#### Table: Heterogeneous effects of the information-only treatment on early childcare and daycare applications and access by SES as measured by the occupation status of the mother (ISEI)


```{r RobustnessHTESESsTableT1ISEIMother,echo=FALSE, results='asis', cache=TRUE,out.width='100%',}
```

#### Table: Heterogeneous effects of the information-only treatment on early childcare and daycare applications and access by SES as measured by the composite index of SES


```{r RobustnessHTESESsTableT1CompositeSES,echo=FALSE, results='asis', cache=TRUE, out.width='100%',}
```


### Information + support treatment

#### Heterogeneous effects of the information + support treatment on early childcare applications

```{r RobustnessHTESESGraphsT2EarlychildcareApp,echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

#### Heterogeneous effects of the information + support treatment on early childcare access

```{r RobustnessHTESESGraphsT2EarlychildcareAccess,echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

#### Table: heterogenous effects of the information + support treatment on early childcare applications and access using the occupation status of the mother (ISEI)

```{r RobustnessHTESESTableT2ECISEIMotherEC,echo=FALSE, results='asis', cache=TRUE, out.width='100%'}
```

#### Table: heterogenous effects of the information + support treatment on early childcare applications and access using the composite index of SES

```{r RobustnessHTESESTableT2ECSES,echo=FALSE, results='asis', cache=TRUE, out.width='100%'}
```



#### Heterogeneous effects of the information + support treatment on daycare applications

```{r RobustnessHTESESGraphsT2DaycareApp,echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

#### Heterogeneous effects of the information + support treatment on daycare access

```{r RobustnessHTESESGraphsT2DaycareAccess,echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

#### Table: heterogenous effects of the information + support treatment on daycare applications and access using the occupation status of the mother (ISEI)

```{r RobustnessHTESESsTableT2DaycareISEIMother,echo=FALSE, results='asis', cache=TRUE}
```

#### Table: heterogenous effects of the information + support treatment on daycare applications and access using the composite index of SES

```{r RobustnessHTESESsTableT2DaycareCompositeSES,echo=FALSE, results='asis', cache=TRUE, out.width='100%'}
```

## Sensitivity analysis of the main results: models

### Classical Ordinary-Least-Squares (OLS) models

We reproduce our results using classical OLS models instead of stacked regressions. The former are more common to analyse RCT results. However, they can introduce contamination bias in the estimates (Goldsmith-Pickham, 2024).

#### Main effects
```{r RobustnessClassicalOLS,echo=FALSE, results='asis', cache=TRUE}
```

#### HTE 

```{r RobustnessOLSHTE,echo=FALSE, results='asis', cache=TRUE}
```

### Logit models

We reproduce our results using logit models. Note that logit models remove fixed effects with homogeneous outcomes (only 0 or only 1) from the analysis, which reduces power.

#### Main effects

```{r RobustnessLogitMainTable,echo=FALSE, results='asis', cache=TRUE}
```

#### HTE

```{r RobustnessLogitHTE,echo=FALSE, results='asis', cache=TRUE}
```




