---
output:
  word_document: default
  html_document: default
---



## The intention-to-action gap in early childcare application and access

We found a systematic pattern of outcome differences among households in the control group across the main dimensions of heterogeneity. Low-SES households, present-orientated households, and households with a lower baseline knowledge of early childcare were less likely to intend to use early childcare at baseline, to submit an application, and to eventually secure access to early childcare (see Figure \@ref(fig:AttentionAction)). Mothers born abroad were just as likely as mothers born in France to intend to use early childcare, yet they applied less often for a childcare spot and secured it less often. Moreover, these gaps increased from intention to application and from application to access. This suggests the existence of social gradients in intention-to-action gaps.  It also highlights additional barriers faced after applications are submitted, further limiting access for underprivileged groups.


```{r AttentionAction, echo=FALSE,out.width='100%', results='asis', fig.height=6, cache=TRUE, fig.cap=" The intention-to-action gap in early childcare application and access in the control group across four dimensions of heterogeneity. Intention to use early childcare is measured at the baseline survey during pregnancy. Early childcare application and early childcare access are measured at the endline survey one year after."}
```


## Main effects of the two interventions

```{r TableITT, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

In Table 2 of the Methods section and in Extended Data Table 10, we report evidence that treated and control groups were equivalent at baseline and not affected by differential attrition. First, intention-to-treat estimates without covariates revealed that the information + support group was 4 percentage points more likely to apply for early childcare than both the control group and those receiving information only. However, accounting for multiple testing, we cannot rule out 0 from the simultaneous confidence intervals (Table \@ref(fig:TableITT), first column; control mean = 0.75; ß = 0.04; Standard Error (SE) = 0.02; 95% Simultaneous Confidence Interval (SCI), (-0.01, 0.09); P = 0.042; adjusted p-value = 0.10). As pre-registered, we used post-lasso regressions to select and adjust covariates. The resulting estimates, presented in Extended Data Table 1, are closely aligned and exhibit greater precision. They confirmed the overall pattern of a positive impact of the information + support treatment on applications (ßpost-lasso = 0.048; SE = 0.019; 95% CI, (0.01, 0.086); P = 0.015; H1b supported). In contrast, the information-only treatment had no impact on applications (ß = -0.01; SE = 0.02; 95% SCI, (-0.06, 0.04); P = 0.762; adjusted p-value = 0.762; H1a not supported; H2a supported). Second, there was no impact of either treatment on the probability of accessing early childcare (see Table 1; H1c, H1d, H2b, and H3c not supported).

Third, the effects of offering information + support on daycare applications specifically were twice as large as the effects on early childcare applications, which suggests that the effects on applications were driven by this specific type of childcare. Households assigned to the information + support treatment were 8 percentage points more likely to apply for daycare centres, which corresponds to a 14% increase (control mean = 0.59; ß = 0.08;  SE = 0.03; 95% SCI, (0.02, 0.14); P = 0.002 ; adjusted p-value = 0.003; H3c supported); and 5 percentage points more likely to access a daycare centre, which corresponds to a 24% increase (control mean = 0.21; ß = 0.05;  SE = 0.02; 95% SCI, (0.00, 0.10); P = 0.027; adjusted p-value = 0.036; H3d supported). The information-only treatment on daycare did not impact applications or access (H3a and H3c not supported). The post-lasso estimates confirmed these patterns (Extended Data Table 1).

Finally, since we recorded whether parents assigned to the second treatment accepted to receive personalised support, we used instrumental variable analyses to estimate the average treatment effects on the treated45. As shown in Extended Data Table 2, the information + support treatment resulted in an 8 percentage-point increase in the probability of applying for compliers (average counterfactual = 0.82; ß = 0.08; SE = 0.04; 95% SCI, (-0.01, 0.17); P = 0.042; adjusted p-value = 0.068). However, we did not find any effect on access (average counterfactual = 0.56; ß = 0.03; SE = 0.05; 95% SCI, (-0.08, 0.14); P = 0.56; adjusted p-value = 0.56). When restricting our analyses to daycares, the information + support treatment led to a 15 percentage-point increase in daycare applications for compliers, which corresponds to a 22% increase (average counterfactual = 0.69; ß = 0.15;  SE = 0.05; 95% SCI, (0.05, 0.26); P = 0.0016; adjusted p-value  = 0.002) as well as a 10 percentage points increase in daycare access, which corresponds to a 53% increase of the counterfactual average (average counterfactual = 0.19; ß = 0.10;  SE = 0.04; 95% SCI, (0.00, 0.19); P = 0.02; adjusted p-value = 0.022). 


##  Heterogeneity of the treatment effects

### Information-only treatment

In line with analyses in the general population, we did not find any statistically significant effect of the information-only treatment on the four subgroups of interest: low-SES households, households with a migration background, households with a lower baseline knowledge, and present-orientated households (see Extended Data Fig. 1, and Supplementary Table 2.1). 

### Information + support

#### Early childcare applications

```{r HetT2ITTATT, echo=FALSE, out.width='100%', results='asis', fig.height=7, fig.cap="Heterogeneous effects of the information + support treatment on early childcare applications and access - Intention-to-treat estimates (ITT) and Average Treatment effects on the Treated (ATT)."}
```

The information + support treatment increased the probability that households apply for early childcare across all dimensions of heterogeneity, as shown in Figure \@ref(fig:HetT2ApplicationITTATT). The average treatment effects on the treated were substantial. Indeed, this intervention nearly closed the application gap for all dimensions. For instance, as shown in Extended Data Table 4, we found a 17 percentage point increase in the probability that low-SES households apply for early childcare (average counterfactual = 0.60; ß = 0.17; SE = 0.08; 95% SCI, (0.00, 0.034); P = 0.024; adjusted p-value = 0.043), and a 42 percentage point increase in the probability that households with low baseline knowledge of early childcare apply for it (average counterfactual = 0.36; ß = 0.42;  SE = 0.20; 95% SCI, (-0.02, 0.86); P = 0.034; adjusted p-value = 0.061).


However, as shown in Figure \@ref(fig:HetT2AccessITTATT) and Extended Data Table 4, effects on access to early childcare remained limited, with significant improvements observed only among households with low baseline knowledge of early childcare. Their probability of accessing early childcare increased by 48 percentage points (average counterfactual = 0.05; ß = 0.48; SE = 0.11; 95% SCI, (0.22, 0.73); P = 0.000; adjusted p-value = 0.000). This suggests that additional barriers hinder low-SES households and households with a migration background from accessing early childcare slots, even after submitting applications.


## Distribution across early childcare types: daycare access

We investigated heterogeneous impacts of the treatments for daycare access. In line with our overall findings, there was no effect of the information-only treatment on application and access to daycare centres (see Extended Data Figure 2 and Supplementary Table 2.2).

```{r HetT2Daycare, echo=FALSE, out.width='100%', results='asis', fig.height=7, fig.cap="Heterogeneous effects of the information + support treatment on daycare application and access - Intention-to-treat estimates (ITT) and Average Treatment effects on the Treated (ATT)."}
```
As shown in Extended Data Table 6, the information + support intervention increased the probability of applying for daycare for both low- and high-SES households, by 18 and 14 percentage points respectively, which corresponds to a 38% and a 21% increase (average counterfactual Low-SES = 0.47; ß = 0.18; SE = 0.06; 95% SCI, (0.02, 0.34); P = 0.015; adjusted p-value = 0.025; average counterfactual High-SES = 0.66; ß = 0.14; SE = 0.07; 95% SCI, (0.00, 0.28); P = 0.032; adjusted p-value = 0.056). However, the impacts on access were limited to high-SES households, which experienced a 16-percentage point increase (average counterfactual High-SES = 0.23; ß = 0.16; SE = 0.05; 95% SCI, (0.04, 0.28); P = 0.005; adjusted p-value = 0.007), as depicted in Figure \@ref(fig:GraphAccessDaycare) and shown in Extended Data Table 6. This increase in daycare access was associated with a 68% reduction in the probability that mothers in these households would decrease their activity levels (average counterfactual = 0.38; ß = -0.23; SE = 0.07; 95% SCI, (-0.38, -0.09); P = 0.0007; Extended Data Table 7).  Furthermore, as observed for early childcare generally, this intervention also led to a 36-percentage point increase in the probability that households with low baseline knowledge accessed daycare specifically (average counterfactual = 0.03; ß = 0.36; SE = 0.10; 95% SCI, (0.13, 0.50); P = 0.0008; adjusted p-value = 0.001).


## Mechanisms: knowledge of the system, feeling of legitimacy, and admission criteria

```{r MechanismsInfo, echo=FALSE, out.width='100%', results='asis', fig.height=8, cache=TRUE, fig.cap= "Heterogeneous effects of the information + support treatment on early childcare applications - Intention-to-Treat estimates (ITT) and Average Treatment Effects on the Treated (ATT)." }
```

The effects of the information + support treatment on early childcare applications, and specifically on daycare applications, were stronger among households that had not previously accessed early childcare (Figure \@ref(fig:Mechanisms) and Extended Data Table 8). For this group, the information + support treatment increased the probability of applying for any early childcare option by 21% (average counterfactual = 0.69; β = 0.16; SE = 0.05; 95% SCI (0.05, 0.28); P = 0.001; adjusted p-value = 0.003), and the probability of applying for daycare specifically by 37% (average counterfactual = 0.59; β = 0.22; SE = 0.05; 95% SCI, (0.1, 0.33); P = 0.000; adjusted p-value = 0.000). These findings suggest that participants who were new to the system and received support were helped in learning “the rules of the game" and navigating the early childcare system. However, we did not observe any effect of the treatment on knowledge of the early childcare system (e.g. the different types of early childcare), as shown in Supplementary Table 3.1.

```{r MechanismsPsych, echo=FALSE, out.width='100%', results='asis', fig.height=8, cache=TRUE, fig.cap= "Heterogeneous effects of the information + support treatment on early childcare applications - Intention-to-Treat estimates (ITT) and Average Treatment Effects on the Treated (ATT)." }
```

Mothers who were inactive at baseline also applied more. For this subgroup, the information + support treatment increased the probability of applying for any early childcare by 80% (Figure \@ref(fig:Mechanisms), average counterfactual = 0.4; ß = 0.32; SE = 0.1; 95% CI, (0.09, 0.54); P = 0.001; adjusted p-value = 0.004). For daycare, additional analyses in Extended Data Table 9 showed a similar pattern, regardless of their SES (average counterfactual Inactive & Low-SES = 0.33; ß = 0.25; SE = 0.011; 95% SCI, (-0.01, 0.50); P = 0.025; and average counterfactual Inactive & High-SES= 0.36; ß = 0.48; SE = 0.25; 95% SCI, (-0.08, 0.99); P = 0.036). However, the effects on access to daycare were concentrated among high-SES households in which the mother was active at baseline (average counterfactual = 0.27; ß = 0.16; SE = 0.07; 95% SCI, (0.00, 0.31); P = 0.027; adjusted p-value = 0.045). 

## Robustness checks

To ensure the robustness of the findings, we tested alternative definitions of socioeconomic status. Specifically, we considered mother's occupation using the International Socio-Economic Index of Occupational Status (ISEI) and a composite SES score that accounts for the highest occupation score and the highest education level in the household. These alternative measures yielded similar results compared to using the level of education of the mother (see Supplementary Information Section 4.1). Additionally, we replicated our analyses using logistic regressions and found that the conclusions remained consistent (see Supplementary Information Section 4.2). 
