---
output:
  word_document: default
  html_document: default
---



## The intention-to-action gap in early childcare application and access

WOur descriptive analyses confirm systematic patterns of outcome differences among households in the control group across SES and migration backgrounds. Despite high baseline intentions to use early childcare (81% on average), substantial disparities emerged in both application and access rates by SES and migration background. While 71% of low-SES households and 77% of households with a migration background intended to use early childcare, they were significantly less likely to apply for and access it compared to high-SES households and households born in France, respectively (see Figure \@ref(fig:AttentionAction) and Supplementary Tables 2.11 & 2.12). These gaps widened at each process step - from intention to application and application to access - suggesting both barriers in translating intentions into applications and structural barriers in converting applications to access. Notably, while mothers born abroad showed similar intentions to use early childcare as mothers born in France, they were less successful in applying for and securing spots, highlighting the disproportionate impact of administrative and structural barriers on specific demographic groups. 


```{r AttentionAction, echo=FALSE,out.width='100%', results='asis', fig.height=6, cache=TRUE, fig.cap=" The intention-to-action gap in early childcare application and access in the control group across four dimensions of heterogeneity. Intention to use early childcare is measured at the baseline survey during pregnancy. Early childcare application and early childcare access are measured at the endline survey one year after."}
```


## Main effects of the two interventions

```{r TableITT, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```


In Table 2 of the Methods section and Extended Data Table 7, we report evidence that treated and control groups were balanced at baseline and no evidence of differential attrition. First, intention-to-treat (ITT) estimates revealed that the information + support group was 4 percentage points more likely to apply for early childcare than both the control group and those receiving information only. However, accounting for multiple testing, we cannot rule out 0 from the simultaneous confidence intervals (Table \@ref(fig:TableITT), first column; control mean = 0.75; ß = 0.04; Standard Error (SE) = 0.02; 95% Simultaneous Confidence Interval (SCI), (-0.01, 0.09); P = 0.042; adjusted p-value = 0.10). As pre-registered, we used post-lasso regressions to select and adjust covariates. The resulting estimates in Extended Data Table 1 are more precise. They confirmed the overall pattern of a positive impact of the information + support treatment on applications (ßpost-lasso = 0.048; SE = 0.019; 95% CI, (0.01, 0.086); P = 0.015; H1b supported). In contrast, the information-only treatment had no impact on applications (information-only vs control: ß = -0.01; SE = 0.02; 95% SCI, (-0.06, 0.04); P = 0.762; adjusted p-value = 0.762; H1a not supported; information + support vs. information-only: ß = 0.05; SE = 0.02; 95% SCI, (-0.01, 0.10); adjusted p-value = 0.1; H2a marginally supported). Neither treatment impacted the probability of accessing early childcare (see Table 1; H1c, H1d, H2b, and H3c not supported).


Finally, as we recorded whether parents assigned to the support accepted it, we used random assignment to information + support as an instrument to estimate the average treatment effects on the treated (ATT)[@FrolichMelly2013]. With an average compliance rate of 52% (see Supplementary Table 2), ATT estimates were approximately twice as large as ITT estimates. For instance, the information + support treatment led to a 10-percentage-points increase in daycare access, which corresponds to a 53% increase relative to the counterfactual average (average counterfactual = 0.19; ß = 0.10; SE = 0.04; 95% SCI, (0.00, 0.19); P = 0.02; adjusted p-value = 0.022). 


##  Heterogeneity of the treatment effects

### Information-only treatment

In line with analyses in the general population, we did not find any statistically significant effect of the information-only treatment on low-SES or immigrant households (see Extended Data Fig. 1 and Supplementary Table 3.1). 
### Information + support

```{r HetT2ITTATT, echo=FALSE, out.width='100%', results='asis', fig.height=7, fig.cap="Heterogeneous effects of the information + support treatment on early childcare applications and access - Intention-to-treat estimates (ITT) and Average Treatment effects on the Treated (ATT)."}
```

As predicted, the information + support treatment increased the probability that both low-SES and immigrant households applied for early childcare, as shown in Figure \@ref(fig:HetT2ITTATT) (H4a and H5a supported). For compliers, the intervention nearly closed the application gap: as shown in Figure 3 and Extended Data Table 3, we found a 17-percentage-point increase in the probability that low-SES households apply for early childcare (average counterfactual = 0.60; ß = 0.17; SE = 0.08; 95% SCI, (0.00, 0.034); P = 0.024; adjusted p-value = 0.043), and a 15-percentage point increase in the probability that immigrant households do so (average counterfactual = 0.67; ß = 0.15;  SE = 0.06; 95% SCI, (0.01, 0.28); P = 0.018 adjusted p-value = 0.026). However, as shown in Figure 3 and Extended Data Table 3, these increased application rates did not translate into increased access (H4b and H5b not supported), which suggests that additional barriers hinder access for low-SES and immigrant households, even after submitting applications.



## Distribution across early childcare types: daycare access

We investigated the heterogeneous impacts of the treatments for daycare access. The information-only treatment did not affect the application and access to daycare centres (see Extended Data Figure 2 and Supplementary Table 3.2).

```{r HetT2Daycare, echo=FALSE, out.width='100%', results='asis', fig.height=7, fig.cap="Heterogeneous effects of the information + support treatment on daycare application and access - Intention-to-treat estimates (ITT) and Average Treatment effects on the Treated (ATT)."}
```


As shown in Figure 4 and Extended Data Table 4, the information + support intervention increased the probability of applying for daycare for both low- and high-SES households by 18 and 14 percentage points respectively, which corresponds to a 38% and 21% increase (average counterfactual Low-SES = 0.47; ß = 0.18; SE = 0.06; 95% SCI, (0.02, 0.34); P = 0.015; adjusted p-value = 0.025; average counterfactual High-SES = 0.66; ß = 0.14; SE = 0.07; 95% SCI, (0.00, 0.28); P = 0.032; adjusted p-value = 0.056). However, the effects on access were entirely driven by treated high-SES households, who experienced a 16-percentage-point increase in access (average counterfactual High-SES = 0.23; ß = 0.16; SE = 0.05; 95% SCI, (0.04, 0.28); P = 0.005; adjusted p-value = 0.007), as shown in Figure 4and Extended Data Table 4. This increased daycare access was associated with increased mothers’ labour supply at the intensive margin. They experienced a 68% reduction in the probability of decreasing their activity levels (average counterfactual = 0.38; ß = -0.23; SE = 0.07; 95% SCI, (-0.38, -0.09); P = 0.0007; Extended Data Table 5).  

## Robustness checks
We tested alternative measures of SES. Specifically, we considered the mother's occupation using the International Socio-Economic Index of Occupational Status (ISEI) and a composite SES score accounting for the highest occupation score and the highest education level in the household. These alternative measures yielded similar results compared to mothers' education level (see Supplementary Information 5.1). Additionally, we replicated our analyses using logistic regressions and found consistent conclusions (see Supplementary Information Section 5.2). 

## Mechanisms

```{r MechanismsInfo, echo=FALSE, out.width='100%', results='asis', fig.height=8, cache=TRUE, fig.cap= "Heterogeneous effects of the information + support treatment on early childcare applications - Intention-to-Treat estimates (ITT) and Average Treatment Effects on the Treated (ATT)." }
```

Overall, the null effects for the information-only treatment contrasted with the positive effects for the information + support treatment, suggesting that process costs play a significant role in the application gaps. Nevertheless, as shown in Figure 5 and Supplementary Table 4.1,  information costs also played a substantial role in the observed application disparities. First, as pre-registered, the effects of the treatments on households with limited baseline knowledge about early childcare were substantial (H6a and H6b supported). However, estimates are imprecise due to the small sample size. Among this subgroup, the information + support treatment more than doubled compliers’ probability of applying for early childcare (average counterfactual = 0.36; ß = 0.42; SE = 0.08; 95% SCI (-0.01, 0.86); P = 0.034; adjusted p-value = 0.04), and multiplied by nearly 10 their probability of accessing early childcare (average counterfactual = 0.05; ß = 0.48; SE = 0.11; 95% SCI, (0.22, 0.73); P = 0.000; adjusted p-value = 0.000). 

Second, as pre-registered, the information + support treatment also strongly affected households that had never previously used early childcare (H7a and H7b supported). For instance, the information + support treatment increased their probability of applying for daycare by 37% (average counterfactual = 0.59; ß = 0.22; SE = 0.05; 95% SCI, (0.1, 0.33); P = 0.000; adjusted p-value = 0.000; see Supplementary Table 4.2). 
Third, the information + support treatment exhibited more pronounced effects among households where fewer than half of the friends and relatives use early childcare and consequently have fewer social resources to navigate the early childcare system (exploratory analysis that was not pre-registered). For this group, the information + support treatment increased the probability of applying for early childcare by 40% among compliers (average counterfactual = 0.55; ß = 0.22; SE = 0.08; 95% SCI (0.04, 0.39); P = 0.006; adjusted p-value = 0.01), and the probability of accessing early childcare by 58% (average counterfactual = 0.31; β = 0.18; SE = 0.08; 95% SCI, (0.01, 0.36); P = 0.02; adjusted p-value = 0.035). Put together, these findings suggest that the treatment helped participants who were new to the system learn “the rules of the game" and navigate the early childcare system. However, we did not detect any treatment effect on general knowledge about early childcare, as shown in Supplementary Table 4.3. Therefore, the increase in applications likely does not stem from enhanced general knowledge captured by these measures, such as the different types of early childcare, but rather from an increased understanding of subtle information that we could not measure in the questionnaire, such as the timing of application.

```{r MechanismsPsych, echo=FALSE, out.width='100%', results='asis', fig.height=8, cache=TRUE, fig.cap= "Heterogeneous effects of the information + support treatment on early childcare applications - Intention-to-Treat estimates (ITT) and Average Treatment Effects on the Treated (ATT)." }
```

Our results suggest that the intervention also alleviated some psychological costs, as shown in Figure 6 and Supplementary Table 4.3.1. First, our results are stronger for present-biased individuals. For present-biased compliers, the information + support treatment increased by 17 percentage points their probability of applying to early childcare (average counterfactual = 0.66; ß = 0.14; SE = 0.07; 95% SCI (-0.01, 0.29); P = 0.03; adjusted p-value = 0.066). 

Second, even though neither of the treatments mentioned the potential benefits of childcare, the intervention proved more effective for participants who exhibited low trust in early childcare at baseline (exploratory analysis that was not pre-registered). Specifically, the intervention tripled the probability of securing a spot among low-trust compliers (average counterfactual = 0.12; ß = 0.36; SE = 0.02; 95% SCI, (0.01, 0.71); P = 0.02; adjusted p-value = 0.037) but had no impact on high-trust households. 

Third, mothers who were inactive at baseline applied more, which suggests they felt more legitimate in applying. For this subgroup, the information + support treatment increased this probability by 80% (average counterfactual = 0.4; ß = 0.32; SE = 0.1; 95% CI, (0.09, 0.54); P = 0.001; adjusted p-value = 0.004). For daycare, additional analyses in Extended Data Table 6 showed a similar pattern, regardless of their SES (average counterfactual Inactive & Low-SES = 0.33; ß = 0.25; SE = 0.011; 95% SCI, (-0.01, 0.50); P = 0.025; and average counterfactual Inactive & High-SES = 0.36; ß = 0.48; SE = 0.25; 95% SCI, (-0.08, 0.99); P = 0.036; exploratory analysis that was not pre-registered). However, the effects on access to daycare were concentrated among high-SES households in which the mother was active at baseline (average counterfactual = 0.27; ß = 0.16; SE = 0.07; 95% SCI, (0.00, 0.31); P = 0.027; adjusted p-value = 0.045). 

