---
output:
  word_document: default
  html_document: default
---

## Ethics information

This experiment was approved by the Institutional Review Board of the Paris School of Economics (IRB Number: 2022-015). Participants explicitly consented to the study at the beginning of each survey and were offered a 10 EUR (about 11 USD) voucher after completing the endline.

## Design

### Study setting

*The French early childcare system*
France operates a dual early childhood education and care system that differentiates between early childcare services for children aged 0-3 years and preschool education for those aged 3-6 years. Preschool (*école maternelle*) is free of charge, universal, and mandatory from the age of three, ensuring nearly universal access for children in this age group. In contrast, early childcare services for children under three years comprise diverse facilities. Formal care options, referred to as "early childcare" in this article, encompass regulated childminders (assistantes maternelles), collective daycare centres (*crèches*), and private nannies. Local administrations may operate daycare centres -typically municipalities- non-profit organisations, or private enterprises.

Early childcare quality is regarded as high by international standards in this country, yet notable heterogeneity exists between childminders and daycare centres[@ONAPE2023]. Care provision begins significantly earlier than in many other countries, and evidence concerning the effects of very early care remains mixed within the international literature3,62. Analyses examining the effects of early childcare in France are limited. Some correlational studies indicate positive associations between access to daycare before age one and improved language skills by age two[@Grobon2018] A study employing panel data and variations in birth quarters, along with relative local childcare supply as an instrument for access to daycare at age one, reports substantial positive effects on language proficiency at age two, particularly for children from low-SES backgrounds and those from immigrant households[@BergerEtAl2021a]. The study also indicates overall positive effects on motor skills for these subgroups, although some of these effects are non-significant; furthermore, it reveals smaller and negative impacts on behaviour—albeit mostly non-significant for these subgroups—contrasting with correlational studies that demonstrate fewer behavioural difficulties in children who attended early childcare during middle school24. These latter discrepancies may reflect that children experience increased behavioural problems in the short term due to the novel situation of being cared for by strangers. However, these effects tend to become positive in the long term compared to children who did not experience formal education and care before school entry24,61.

Despite France’s relatively high rates of early childcare provision compared to other OECD countries, significant access disparities exist, mainly according to SES and migration background. High-income households are more likely to access early childcare than low-SES households, with 70% of high-income families using early childcare in 2021 compared to only 23% of low-income families64. Similarly, the enrolment rate for recently arrived non-EU migrant children aged 0–2 in formal childcare was only 18%, compared to 38% for the general population in 201819. These disparities are further exacerbated by the decentralised and fragmented nature of the childcare system, which varies significantly across municipalities regarding availability, allocation criteria, and access to information.
While formal childcare services are available as early as 2.5 months after birth—coinciding with the end of statutory maternity leave—parents who have worked for at least two years can opt for parental leave. The duration of this leave varies based on the number of children: from six months for the first child to up to forty-eight months from the third child onwards. However, the low flat-rate compensation (approximately 448 EUR, equivalent to 467 USD, per month in 2024) renders this option primarily accessible to low-income households or secondary earners, as it constitutes a substantial income loss for most working parents65. Approximately 50% of children under three years of age in 2021 were in parental or informal care64. Enrolment rates in early childcare substantially increase between six months and one year. While 17% of children under six months are enrolled in early childcare, this proportion quickly rises to 52% between six months and one year after birth. It then remains relatively constant throughout the following two years59,65.

Indeed, childcare slots are allocated predominantly before the age of one. Therefore, parents should submit their application very early—preferably during the early stages of pregnancy. Additionally, parents are often required to reapply to keep their position on waiting lists if they do not receive a slot initially. While it is technically possible to get a slot after age one, it is much more difficult because most slots are filled by younger babies, who then stay in the system. The daycare application process is also synchronised with the academic year, which means that a substantial number of slots for infants under one-year-old are allocated in June for enrolment starting in September. This timing significantly limits opportunities for mid-year enrolment and generates disparities in access based on the month of birth66. This specific context underscores the necessity of our intervention being as early as during pregnancy. 

Due to excess demand relative to supply, facilities often have long waiting lists67, and in most municipalities, providers distribute the existing spots based on priority rules. These rules are not mandatory and are left to the discretion of the municipalities. Thus, they may or may not be publicly available to parents59,68. The law only mandates higher priority for applicants with disabled children, those involved in social and professional integration processes, and families referred by social services (Article L.214-7 of the French Family and Social Action Code). Beyond that, each municipality determines its own priority rules. Although recent national policy guidelines discourage employment status as a priority rule, it is currently unclear to what extent it is still a common practice to prioritise dual-earner households—a criterion historically implemented to support work-family balance. This employment-based prioritisation can systematically disadvantage low-income families, who often face unstable employment situations. The government has introduced financial mechanisms to promote socioeconomic diversity, including the Social Mixity Bonus (Bonus Mixité Sociale) and the AVIP certification (Aide à la Vocation d'Insertion Professionnelle), which provide additional funding to facilities that enrol higher proportions of low-SES children. However, since facilities maintain considerable autonomy in their selection processes, implementing these diversity-promoting measures may vary substantially across locations.


*Local supply-side dynamics*
Our study takes place in the Paris metropolitan area and includes 84 municipalities across three provinces, called *Départments* in France (Paris, Val de Marne, and Seine Saint Denis). Despite being geographically close and having similar high population densities, these three provinces differ regarding the availability of early childcare slots and application processes. In Paris, daycare slots are allocated at the district level (*arrondissement*), and the availability of early childcare slots is the highest in the country. In 2021, there were, on average, 80 early childcare slots available per 100 children aged 0-3 years64. Val-de-Marne often centralise the application process at the city level, and the availability of early childcare slots is about the same as the national average. In 2021, there were 52.6 slots per 100 children aged 0-3 years in this province, while the national average was 59.1.

Importantly, in this region, most applications for public daycare go through a website with no mobile version. Seine-Saint-Denis has one of the country's lowest coverage rates of early childhood services. In 2021, there were, on average, 35 early childcare slots per 100 children aged 0-3 years in this province. Seine Saint Denis primarily organises application processes at the municipality level, with sharp territorial inequalities. In Supplementary Information Section 1, we provide a more detailed description of the early childcare supply in these areas and compare it to national averages. 

Notably, the relative proportions of the various childcare options differ in our study compared to other regions in France, particularly rural areas. In 2021, childminders provided an average of 27.3 slots per 100 children aged 0-3 years in France, while daycare centres accounted for 26 slots. However, within the context of our study, daycare centres are the primary providers of formal childcare, thereby justifying our specific focus on this type of service in both the treatment design and analyses. In Paris, where total childcare coverage is the highest, there was an average of 54.5 daycare slots per 100 children aged 0-3 years in 2021, in contrast to only 4.9 slots per 100 children for childminders. Similarly, in Val-de-Marne, daycare centres constitute most of early childcare coverage (30.5 slots per 100 children), with childminders having a more secondary role (13.8 slots per 100 children). In Seine-Saint-Denis, where childcare coverage is the lowest, daycare centres dominate the formal care landscape, offering 22.2 slots per 100 children compared to 12.1 for childminders.

### Research design

Between September 17th and December 16th, 2022, we contacted pregnant mothers (four to nine months of pregnancy) during their visits to maternity wards of hospitals in the Paris metropolitan area. We administered a baseline questionnaire to collect information on socio-demographic characteristics, knowledge of the French early childcare system, and intentions to use early childcare. 2027 questionnaires were administered, but only 1849 were retained for the study because of inclusion criteria: 103 respondents were undocumented and did not have a partner allowed to stay on the French territory, meaning that they could not access early childcare services even with our support, and 70 declined to provide their phone number. We excluded nine additional participants due to various reasons, such as non-functioning phone numbers. 

One year later, between October 16th and December 23rd, 2023, participants were called back to answer the endline questionnaire through assisted telephone interviews. Of the 1849 households that had been randomised, 79% of them completed the Endline survey (1455 out of 1849). Robustness analyses and balance checks show that selective attrition does not affect the experimental results (see Extended Data Table 10).


Map 1 illustrates the distribution of the endline sample across the Paris metropolitan area.

```{r MAP, echo=FALSE, fig.cap="Distribution of the sample across the Paris metropolitan area", fig.width = 10 ,fig.height = 10}
```

### Intervention design

Neither the information-only nor the information + support treatments were prescriptive about childcare choices. The goal of the intervention was to help households make informed choices on their own, with or without guidance and assistance with formal applications. The treatment arms are as follows:

-   ***Information treatment***: *October-December* 2022: this treatment involves two clusters of contents

    -   [*Information about early childcare types*]{.underline}: information aimed at helping households to identify which type of early childcare fits best with their preferences and constraints. Treated households received a text message linking to a short video presenting information about the availability and characteristics of different early childcare options and how they fit different preferences and needs. In the following days, a second text message linked to a second short video presenting early childcare eligibility criteria and costs and a third video presenting less well-known early childcare options (halte-garderies), which may be particularly well-suited to low-SES households (collective but less intensive care, less restrictive criteria of access, easier application procedures and more flexible time schedules).

    -   [*Information about the application process*]{.underline}: information aimed at understanding the application process. As for the information about early childcare types, this involved sending text messages linking to videos presenting information on the calendar of applications, application procedures, and tips to maximise one’s chances of success, such as applying for multiple early childcare options. The content of the first video  was tailored to the area in which households live, because each area has a specific application process. We also gave households access to a website with resources to help them navigate the application process (e.g. checklists, detailed information on the application process at the city level, contract templates).

    -   [*Reminders*]{.underline}: Reminders were sent by text messages in the third week of treatment. Around February 2023, households received a personalised reminder to watch the video and our content to maximise applications for the June commission, where most of the slots get allocated. The content of the message was personalised according to their planned early childcare choices (if and when they were willing to use early childcare) collected at Baseline. We also sent generic reminders to apply shortly before the deadline for the 2023 applications to early childcare (May 2023).

-   ***Information + support treatment***: *February-April 2023*: This treatment involved the same intervention as the information-only treatment according to the same timeline, but also one or several phone calls with parents between February and April 2023 to deliver personalised assistance, as well as personalised application reminders. Between February and April, every two weeks, we randomly allocated the household of this treatment arm to one of the 7 trained research assistants for personalised assistance. Research assistants then called each household as many times as necessary to reach them. The personalised administrative support was then delivered according to a systematic procedure, in French, English or Arabic. The first step was to present the various types of support we could offer to parents. When parents showed interest, we first established a diagnosis of their choices, intentions, and needs after birth. Households were at very different stages of their decision making and we adapted the intervention accordingly. When they had not decided yet, we helped them identify the early childcare solution that best fitted their needs, including how accessible each solution was given their situation, and how affordable each solution was through cost simulations. When they had identified the type of early childcare they wanted, we assisted them according to their demands. Some parents just needed help to identify the early childcare facilities they could apply to, while others needed us to fill the application forms with them. 

-   ***Control group***: Households assigned to the control group received a placebo treatment. Our goal was to maintain some contact with these households in order to minimise attrition at endline. Placebo messages were also sent to the two intervention groups for the same reason. The placebo messages were about events throughout the year (e.g. welcoming text, winter and summer holidays, new year), and useful tips not affecting the outcomes of interest (e.g. flea markets around Paris). Moreover, the households in the control group also received videos, but not about early childcare. The content of these videos referred to emotions and well-being during pregnancy and other health-related topics.

## Sample characteristics

In France, early childcare services welcome children from 3 months to 3 years, and many settings accept registrations long before birth. We thus targeted pregnant women in their fourth through ninth months of pregnancy. We recruited expectant mothers through face-to-face interviews in 8 maternity wards in the Paris metropolitan area. Figure 6 shows the distribution of our endline sample across the Paris region. Our sampling strategy resulted in a low refusal rate, with 99.5% of mothers agreeing to participate in the study. To be eligible, parents needed to be at least 18 years old (99.7% of the interviewed individuals), have at least one partner allowed to stay on French territory (96%), possess a smartphone (98.9%), and demonstrate a basic level of comprehension and communication in French, English, or Arabic (98% of the population in these areas). Even among low-SES and immigrant families, possessing a smartphone and having a basic level of comprehension and communication in French is not particularly restrictive69. More than nine low-SES families out of ten have a smartphone, and more than nine immigrant individuals understand French69,70. 

```{r BalanceTable, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

## Variable description

### Main outcomes

The endline survey included our primary outcome variable, a binary variable that takes the value 1 if the household has applied to at least one early childcare facility and 0 otherwise. Our secondary outcome variable is access to early childcare. This variable takes the value 1 if the family has secured a slot in any early childcare facility, indicating that the child is enrolled or about to enrol in a facility. To ensure the reliability of our findings, we asked parents to provide the name(s) and address(es) of the early childcare facilities to which they had applied or in which their child had enrolled. Additionally, we incorporated the questions on early childcare access within a broader questionnaire that covered various aspects of maternal and newborn care unrelated to early childcare, such as breastfeeding, health behaviours during pregnancy, newborn health, and maternal mental health.

### Heterogeneity

All treatment heterogeneity variables were measured during the baseline survey. SES was primarily assessed based on mother’s level of education. Our main indicator of SES was a binary variable indicating whether the mother had completed tertiary education. We conducted robustness checks using alternative measures of SES, including: 1) Mother's occupation, coded according to the International Standard Classification of Occupations (ISCO-08) using the 3-digit level and then recoded into a numerical score using the International Socio-Economic Index of Occupational Status (ISEI) with the R software package occupar71,72. Finally, we constructed a variable that takes the value 1 if the ISEI score of the mother is above the median ISEI score in the sample and 0 otherwise; 2) A composite SES score that takes into account the highest occupation level in the households and the highest education level in the household, using a method similar to the one used by the OECD for the PISA survey[@OECD2020; @Avvisati2020a]. Each mother and father's level of education was converted into equivalent years of education ranging from 0 (no degree) to 17 (Master's degree and above). Mothers' and fathers' occupations were both coded according to the aforementioned procedure. 

Migration background was measured by a variable that takes the value 1 if the mother was born outside French territory and 0 otherwise. The baseline level of knowledge was initially coded as a categorical variable with four levels: poor, fair, good or excellent level of knowledge. As pre-registered, we used this initial variable to create a binary variable that takes the value 1 if the family has a poor level of knowledge at baseline and 0 otherwise. The activity level of the mother was also measured using a binary variable, with a value of 1 indicating that she was employed, regardless of whether she was on parental leave for a previous child or a student at the time of the baseline interview, and a value of 0 indicating otherwise. Another binary variable was used to assess previous early childcare access, with a value of 1 indicating that one of the parents had accessed early childcare services in the past for any of their children and a value of 0 indicating otherwise. Lastly, following the approach of Reimers et al. (2009), temporal orientation was measured by asking mothers to choose between a hypothetical reward of 50€ in three days or 80€ in three months. The resulting variable, present orientation, was coded as 1 if the mother chose the 50€ reward[@ReimersEtAl2009].

To measure descriptive norms, we asked participants to report the proportion of their friends and relatives who use early childcare services. To ensure sufficient observations in each category, we combined responses indicating that “all” of their friends and relatives use early childcare with those indicating that “most” of their friends and relatives do so. We then created a dummy variable that takes the value 1 if the household fell into one of these two categories and 0 otherwise. Lastly, to assess trust in early childcare facilities, participants were asked to indicate their level of agreement with the statement, “In general, I trust early childcare facilities to take care of my child,” using a five-point scale ranging from “strongly disagree” to “strongly agree.” We then recoded this question into a dummy variable that takes the value of 1 if participants answered “agree” or “strongly agree”.


## Analysis plan 

### Randomisation protocol

To improve precision and ensure balance on a set of characteristics likely to affect our main outcomes, we used block-random assignment based on the cross-product of i) Education of the mother (“tertiary”/“secondary or lower”), ii) Intention to use early childcare (“no”/“yes but has never used early childcare before”/“yes and already has used early childcare before”), and iii) Supply (early childcare coverage rate higher/lower than the average in the department).  

We collected data over three months, during which we defined "waves" as two-week intervals for implementing the assignment procedure. Ultimately, our design comprised six randomisation waves, each containing three assignment conditions across the 12 blocks of each lottery, resulting in 72 block-wave fixed effects, hereinafter referred to as “blocks”.


### Assignment probabilities

Each household from the baseline sample had a 1/3 probability of being assigned to one of three groups: control, information-only, or information + support. We employed a single-blind experimental design, ensuring no participant was aware of their treatment status or the alternative treatments. Since our analyses compared pairs of assignment conditions (e.g. information-only vs. control), we relied on conditional assignment probabilities that excluded one treatment arm. However, some blocks had a small or odd number of observations, potentially resulting in slight variations in assignment probabilities across groups. To account for this, we followed Hirano et al. (2003) and estimated a probit assignment model on block-fixed effects in subsamples of pairwise comparisons75. We then used the predicted probabilities from these models as propensity scores, denoted as $p_{ibs}$ , where ibs denotes the household $i$ of block $b$ in sub-sample of pairwise comparison $s$. With these, we define inverse propensity score weights $w_{ibs}=\frac{Z_{ibs}}{p_{ibs}}+\frac{(1-Z_{ibs})}{(1-p_{ibs})}$ and centered assignment $\tilde{Z}_{ibs}=Z_{ibs}-p_{ibs}$ where $Z_{ibs}$ is a dummy that equals 1 when the household $i$ of block b has been assigned to the treatment group in subsample $s$.



## Intention to treat : main average effects

Because we have two treatment arms, we followed Goldsmith-Pickham (2024) and used stacked regressions to estimate the average difference between each pair of assignment condition $S_i \in \{\text{'Information only-Control’}, \text{'Information + support-Control’}, \text{‘Information + support-Information only'}\}$, while avoiding contamination bias in our estimates. We used the following equation: 

$$
Y_{ibs}=\sum_s\sum_b \gamma_{bs} B_{ib}+\sum_s\beta_sZ_{ibs}+\varepsilon_{ibs}
$$

Where Y denotes the outcome of individual $i$ of block $b$ in sub-sample $s$ ; $B_{ibs}$ denotes block-wave dummies and are interacted with $S_{is}$, a factor variable of sub-sample pairs of treatment arms. $Z_{ibs}$ is a dummy that equals 1 when the household $i$ of block $b$ has been assigned to the treatment group in sub-sample $s$. The estimates of $\beta_s$ correspond to the average intention to treat effect [@AtheyImbens2017]. Following Chaisemartin-Ramirez (2022) and  Abadie Et. Al. (2022), we used cluster-heterosckedasticity-robust standard errors adjusted at the block level [@deChaisemartinRamirez-Cuellar2020;@AbadieEtAl2022].This adjustment is very conservative as shown by Abadie Et. Al. (2022), and the detected effects correspond to the lower bound one could expect given these treatments [@AbadieEtAl2022].

### Robustness checks

As pre-registered, we assessed the robustness of our results using a data-driven selection of potential confounders with post-lasso method, i.e. 1) tuning lasso regressions of the outcome on the full set of demeaned covariates and their interactions using 10-fold cross-validation, 2) running a lasso regression with the cross-validated penalty parameter, 3) collecting covariates with non-zero coefficients, and 4) estimating treatment effect models with these covariates in the right-hand side.  For that, we estimated the so-called “pooled regression”:

$$
Y_{ibs}=\sum_s\sum_b \gamma_{bs} B_{ibs}+\sum_s\beta_sZ_{ibs}+\sum_s\mathbf{\dot{X}^\prime}\rho_s+\upsilon_{ibs}
$$


With $\mathbf{\dot{X}}$, the matrix of covariates selectedselected by the lasso method. Lasso selection and estimations were performed separately for each comparison pair, and inference was based on point-wise standard errors clustered at the block level. As the recent work of Negi and Wooldridge (2021)  emphasised, adding the variables  $\mathbf{\dot{X}}$ do not change the probability limit given random assignment80. Therefore, pooled regressions are not meant to correct bias or improve consistency but to improve efficiency. 
We also replicated our primary analyses using a linear probability model with one dummy for each treatment arm, strata fixed effects, and logistic regressions.

## Local average treatment effect of administrative support
Out of the households that were offered support, 52% opted for it on average (See Extended Data Table 2). Thus, assuming that offering support has no effect on outcomes but through the provided support (exclusion restriction), using assignment to the information + support treatment as an instrument for compliance with support can retrieve the Local average treatment effect (LATE) of this treatment81. Besides, administrative support was only offered to those assigned to the information + support treatment, making non-compliance one-sided. Therefore, the monotonicity assumption holds, allowing an “average treatment effect on the treated” (ATT) interpretation of the instrumental variable estimand[@FrolichMelly2013;@ImbensAngrist1994]. We denoted $D_{ib}=1(\text{received support})$ the compliance status and estimated the average treatment effect on the treated through the following system of equations using weighted TSLS:

$$
TSLS~\left\{ \begin{array}{ll}
Y_{i}=&\sum_b \alpha_{b}B_{i}+\delta D_{i}+\mu_{i}\\
D_{i}=& \sum_b \gamma_{b}B_i+\tilde{Z}_{i}\pi_{b}+\epsilon_{i}\\
\end{array} \right. 
$$

Where the instrument $\tilde{Z}_{ib}$ is the centred assignment previously defined.  The coefficient π_s is the average first-stage effect. As Borusyak et al. (2024) showed, this model retrieved a weighted average of block-specific treatment effects82.  We used cluster-robust standard errors adjusted at the block level. The coefficient s retrieves the ATT under the exclusion restriction.


## Average potential outcome of untreated compliers
We estimated the average potential outcomes of untreated compliers using results from Abadie (2003) and Frölich and Melly (2013)53,83. Under the same set of hypotheses, the average potential outcome for untreated compliers is identified, and so is any measurable function 𝑔(⋅) of that potential outcome, as long as 𝑔(⋅) has a finite first moment. Formally:
 
Thus, to compute the probability that untreated compliers - parents who would have accepted administrative support had it been offered to them - applied to any childcare, we define 𝑔(⋅)=(1−𝐷𝑖)𝑌𝑖 and run the same TSLS as before with (1−𝐷𝑖)𝑌𝑖 as outcome and (1−𝐷𝑖) instrumented by $\tilde{Z}_{ib}$ with block fixed-effects.

## Conditional average treatment effects

As pre-registered, we conducted subgroup analyses to elucidate the underlying mechanisms and to assess whether different populations respond to the treatment in ways that align with our theoretical framework. We estimated average treatment effects for pre-specified subgroups using the same estimation strategy that was employed in the main models presented above. We obtained conditional average effects by employing fully saturated stacked regressions, which involved interacting all right-hand side variables with subgroup dummy variables[@Goldsmith2022]. We estimated a first stage for each subgroup in the two-stage least squares models. While these estimations are widely used in the literature, they cannot be interpreted as causal effects due to the non-random manipulation of the subgroups. Rather, they provide valuable insights into potential mechanisms.

# Inference and tests
In the main analyses, we jointly estimated the differences in the three pairwise comparisons of treatment arms for each outcome, along with cluster-heteroskedasticity-robust standard errors adjusted at the block level to account for the correlation in potential outcomes within blocks. We adjusted p-values and confidence intervals to account for the Family-Wise Error Rates (FWER) using the Young-Westfall method implemented by the R package multcomp[@BretzEtAl2010].. For each outcome, our multiple testing procedure adjusted the p-values and confidence intervals for simultaneous inference on the three comparisons (information-only vs. control, information + support vs. control, and information-only vs. information + support).
We also ran Chi-2 tests (also called Wald tests) with the null hypothesis that there was no association between treatment assignment and outcomes against at least one significant difference. We reported the test statistics and associated p-values at the bottom of regression tables85,86. The Chi-2 is slightly more conservative than the F-test (which converges to the Chi-2 test in large samples).
In the heterogeneous treatment effect analyses, we adjusted p-values and confidence intervals using the same method for simultaneous inference on all conditional treatment effects. 
In the balance checks, we did not control for the FWER but for the false discovery rate (FDR) using the Benjamini & Yekutieli method87. 


## Pre-registration
This project has been pre-registered. Its detailed pre-registration is available on the AEA Social Science Registry ([RCT ID AEARCTR-0009901](www.socialscienceregistry.org/trials/9901)). The initial pre-registration was completed on September 27th, 2022. The detailed analysis plan was uploaded on October 18th, 2023, with further details on the theory of change, hypotheses and predictions, the main dimensions of heterogeneity, and the chosen correction for multiple hypothesis testing.

## Deviations from the pre-analysis plan
First, our pre-analysis plan specified examining intervention effects on application behaviours, including the number of applications submitted and their temporal distribution. However, we encountered significant measurement issues during the endline data collection, as parents demonstrated considerable difficulty in accurately recalling their applications' precise timing and quantity. Given these data quality concerns, we followed Lakens (2024) and focused on more reliably measured outcomes to ensure the robustness of our findings88. Second, we initially pre-registered mothers’ activity as a robustness check for our heterogeneity analyses based on SES. However, in light of the relevance of mothers’ activity status in the slot allocation process (see Study Setting in the Methods section), we ultimately conceptualised it as a distinct dimension of heterogeneity. Third, our pre-analysis plan emphasised the necessity for stronger assumptions in instrumental variable estimations when using the control group as the reference group rather than the information-only treatment group. In particular, one must assume that potential compliance with the support does not depend on the information treatment. Nonetheless, due to the absence of any observed effect from the information-only treatment—which renders this additional exclusion restriction more plausible—we chose to mainly concentrate on the comparison between the information + support treatment group and the control group in the main text for the sake of conciseness, which also facilitates interpretation.

## Power calculations

We conducted ex-ante power calculations derived from the existing literature and the PowerUp software. Based on these calculations, we determined that a minimum sample size of 1687 families was necessary to achieve a Minimum Detectable Effect Size (MDES) of d = 0.15, with a 5% first-type error rate, 80% statistical power, and a 25% attrition rate, which is what we pre-registered. This MDES corresponded to a 6-percentage point increase in application rates. However, we were able to randomise more participants than initially anticipated (N = 1,849) and experienced a lower attrition rate of 21%. Consequently, we ultimately achieved an average sample size per treatment arm twice as large as that of Hermes et al. (2021), the only comparable experiment in the literature, while achieving similar effect sizes.
Nevertheless, these preliminary power computations did not account for certain design features. Therefore, we conducted more realistic power calculations using estimates derived from the baseline sample and control groups. We estimated the same models using simulated data across 500 iterations (see Supplementary Information Section 6). Using average treatment effects of .02 for the information-only arm and .06 for the information + support arm, our estimated power was slightly below .8 after considering simultaneous inference and within-block cluster effects. It is important to note that these further power computations were rather conservative since they included fewer blocks and exhibited a lower R² than the actual sample. Overall, this indicates that our study was adequately powered to detect the effects of our treatments.

All analyses were performed using R 4.3.0 and R studio 2023.12.1.
