---
output:
  bookdown::word_document2: default
  html_document: default
  word_document: default
---



<!-- # Extended Data {-} -->



# Post-Lasso estimates of the main outcomes



```{r PostLassoMainTables, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```


#  Average Treatment Effects on the Treated (ATT) of the main outcomes


```{r LATE, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

# Heterogeneous effects of the information-only treatment on early childcare applications and access

```{r T1AccessApplicationGraph,echo=FALSE,results='asis',  fig.width = 9, fig.height = 11,cache=TRUE, out.width='100%', fig.cap="Heterogeneous effects of the information-only treatment on early childcare applications and access - Intention-to-treat estimates (ITT) estimates."}
```


# Heterogeneous effects of the information + support treatment on early childcare applications and access 

```{r TableInfoSupportITTATT,echo=FALSE,out.width='100%', results='asis',message =FALSE, cache=TRUE, fig.cap="Heterogeneous effects of the information + support treatment on early childcare applications - Intention-to-treat estimates (ITT) estimates."}
```

Table \@ref(tab:TableInfoSupportITTATT) presents the heterogeneous treatment effects on the treated and the intention to treat estimates for application and access to early childcare according to our four dimensions of heterogeneity.

- *SES*: We see that the effects on applications to early childcare are concentrated on low-SES households. For them, the information + support intervention increased the probability to apply by 28% for treated households, closing the gap in early childcare application by socio-economic background. However, we see no detectable effect on early childcare access. Even though they applied more, low-SES households were not more likely to access early childcare.

- *Migration background*: The information + support intervention increased the probability that households with a migration background apply for early childcare by 22% for treated households, while not affecting households with no migration background.Therefore, it closed the gap in early childcare application between both types of households for treated households. 

- *Level of baseline knowledge*: The information + support intervention increased the probability that households with a low baseline knowledge about early childcare by 42 percentage points for treated households and access early childcare by 48 percentage points, while having no effect on households who were well-informed at baseline. Interestingly, within the sub-sample of low-informed households, the provision of information alone had a positive impact (see Figure \@ref(fig:T1AccessApplicationGraph)) on access, although it was not as substantial as when combined with administrative support. Households with a low baseline knowledge were also 27 percentage points more likely to access early childcare when treated. These effects on access are quite significant, particularly considering that the probability of accessing an early childcare slot for the control group was only 5%, and not statistically distinguishable from 0. However, it is important to exercise caution when interpreting these results due to the relatively small number of observations within the low baseline knowledge sub-sample (only 227 households).

- *Temporal orientation*: The information + support intervention increased the probability that households in which the mother is present-orientated apply for early childcare by 21% for treated households, while not affecting households with a future-oriented mother, closing the gap in early childcare application by temporal orientation for treated households. However, the treatment had no effect on early childcare access for either group.



# Heterogeneous effects of the information-only treatment on daycare applications and access

```{r DaycareApplicationAccessT1Graph,echo=FALSE, results='asis',message =FALSE, fig.width = 9, fig.height = 11, cache=TRUE, fig.cap="Heterogeneous effects of the information-only treatment on daycare applications and access - Intention-to-treat estimates (ITT) estimates."}
```

# Heterogeneous effects of the information + support treatment on daycare applications and access

```{r DaycareTableInfoSupportITTATT,echo=FALSE,out.width='100%', results='asis',message =FALSE, cache=TRUE, fig.cap="Heterogeneous effects of the information + support treatment on early childcare applications - Intention-to-treat estimates (ITT) estimates."}
```


Table \@ref(tab:DaycareTableInfoSupportITTATT) presents the heterogeneous treatment effects on the treated and the intention to treat estimates for application and access to daycare according to our four dimensions of heterogeneity.

* *SES*: For treated households, the bundle information + support increased the probability to apply for daycare by 38% for low-SES households, but also by 21% for highly-SES households. However, turning to access to daycare, this treatment increased by 70% the probability that highly-SES households accessed daycare, but had no effect on the probability that low-SES households did. 

* *Migration background*:  The information + support treatment increased the probability that households with a migration background apply for daycare by 22% for treated households. Turning to access, the results suggest that the treatment increased the probability that households without a migration background access daycare by 50% for treated households, but the results are only marginally significant.

* *Level of baseline knowledge*: The information + support intervention increased the probability that households with a high baseline knowledge about early childcare by 20% for treated households. The point estimates are about 30 percentage points for low baseline knowledge households, but are not significant, probably due to lack of power. However, it increased by 36 percentage points the probability that households with a low baseline knowledge access daycare. Again, these effects on access are quite significant, particularly considering that the probability of accessing an early childcare slot for the control group was only 3%, and not statistically distinguishable from 0. As a reminder, it is important to exercise caution when interpreting these results due to the relatively small number of observations within the low baseline knowledge sub-sample (only 227 households).

* *Temporal orientation*: The information + support intervention increased the probability that both present-orientated and future orientated households apply for early childcare by 15 percentage points, which represents a 27% and a 23% increase in this outcome respectively. However, it translated in a 18 percentage points increase in the probability that present-orientated households access daycare - a 100% increase in this outcome-, while having no effect on future-orientated households.

# Average effects of the information + support treatment on the probability that the mother reduces her activity by SES

```{r ActivityReduction,echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

# Mechanims: Average effects of the information + support treatment on early childcare and daycare application and access by previous access to early childcare

```{r MechanismsNewcomers,  echo=FALSE, results='asis', cache=TRUE}
```

# Mechanims: Average effects of the information + support treatment on daycare application and access by activity of the mother at baseline and SES
```{r MechanismsActivexSES,  echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

# Attrition

The baseline sample is composed of 1849 pregnant mothers of whom, 1453 answered our endline survey. As a first check, we estimated the means of selected covariates in the baseline sample and in the endline sample to see if the latter has different demographics from the initial sample. We report these estimates in Table \@ref(tab:AttritionTable). Overall, the means computed in the endline sample are very close to those in the baseline sample, with a few significant differences that could well be false positive.

```{r ATTRITIONTable,  echo=FALSE,out.width='100%', results='asis', cache=TRUE, message=FALSE, echo=FALSE}
```
