---
output:
  bookdown::word_document2: default
  html_document: default
  word_document: default
---



<!-- # Extended Data {-} -->



# Post-Lasso estimates of the main outcomes

```{r PostLassoMainTables, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```


#  Average Treatment Effects on the Treated (ATT) of the main outcomes


```{r LATE, echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

# Heterogeneous effects of the information-only treatment on early childcare applications and access

```{r HetT1ITTATT,echo=FALSE, out.width='100%', results='asis', fig.height=7, cache=TRUE, out.width='100%', fig.cap="Heterogeneous effects of the information-only treatment on early childcare applications and access - Intention-to-treat estimates (ITT) estimates."}
```


# Heterogeneous effects of the information + support treatment on early childcare applications and access 

```{r HetT2table,echo=FALSE, out.width='100%', results='asis', fig.height=6, message =FALSE, cache=TRUE, fig.cap="Heterogeneous effects of the information + support treatment on early childcare applications - Intention-to-treat estimates (ITT) estimates and Average Treatment effects on the Treated estimates (ATT)."}
```

Table \@ref(tab:HetT2table) presents the heterogeneous treatment effects on the treated and the intention to treat estimates for application and access to early childcare according to our four dimensions of heterogeneity.

- *SES*: We see that the effects on applications to early childcare are concentrated on low-SES households. For them, the information + support intervention increased the probability to apply by 28% for treated households, closing the gap in early childcare application by socio-economic background. However, we see no detectable effect on early childcare access. Even though they applied more, low-SES households were not more likely to access early childcare.

- *Migration background*: The information + support intervention increased the probability that households with a migration background apply for early childcare by 22% for treated households, while not affecting households with no migration background.Therefore, it closed the gap in early childcare application between both types of households for treated households. 



# Heterogeneous effects of the information-only treatment on daycare applications and access

```{r DaycareApplicationAccessT1Graph,echo=FALSE, out.width='100%', results='asis', fig.height=7, message =FALSE, fig.width = 9, fig.height = 11, cache=TRUE, fig.cap="Heterogeneous effects of the information-only treatment on daycare applications and access - Intention-to-treat estimates (ITT) estimates."}
```

# Heterogeneous effects of the information + support treatment on daycare applications and access

```{r HetT2tableDaycare,echo=FALSE, out.width='100%', results='asis',message =FALSE, cache=TRUE, fig.cap="Heterogeneous effects of the information + support treatment on early childcare applications - Intention-to-treat estimates (ITT) estimates and Average Treatment effects on the Treated estimates (ATT)."}
```


Table \@ref(tab:HetT2tableDaycare) presents the heterogeneous treatment effects on the treated and the intention to treat estimates for application and access to daycare according to our four dimensions of heterogeneity.

* *SES*: For treated households, the bundle information + support increased the probability to apply for daycare by 38% for low-SES households, but also by 21% for highly-SES households. However, turning to access to daycare, this treatment increased by 70% the probability that highly-SES households accessed daycare, but had no effect on the probability that low-SES households did. 

* *Migration background*:  The information + support treatment increased the probability that households with a migration background apply for daycare by 22% for treated households. Turning to access, the results suggest that the treatment increased the probability that households without a migration background access daycare by 50% for treated households, but the results are only marginally significant.

# Average effects of the information + support treatment on the probability that the mother reduces her activity by SES

```{r ActivityReduction,echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```


# Mechanims: Average effects of the information + support treatment on daycare application and access by activity of the mother at baseline and SES

```{r MechanismsActivexSES,  echo=FALSE,out.width='100%', results='asis', cache=TRUE}
```

# Attrition


```{r ATTRITIONTable,  echo=FALSE,out.width='100%', results='asis', cache=TRUE, message=FALSE, echo=FALSE}
```

The baseline sample is composed of 1849 pregnant mothers of whom, 1453 answered our endline survey. Table \@ref(tab:ATTRITIONTable) presents the pairwise comparison of answer rates in the endline by assignment group. Column 1 gives the mean answer rate in the relevant comparison group and Column 2 shows the difference by treatment arm. Models are estimated by OLS with block waves pairwise fixed effect and cluster robust standard error adjusted at the block wave level. On average, 79% of the baseline sample answered the endline survey. The lowest answer rate is the Information-only treatment group with 76% while the highest is among the Information + Support treatment with 80% answers. We use a Chi-2 test of the null hypothesis that all pairwise comparisons are 0 and conclude that answer rates are no different between treatment arms. 
